\begin{thebibliography}{20}
\bibitem{huang_tvlsi2006} Huang et al., ``HotSpot: A Compact Thermal Modeling Methodology for Early-Stage VLSI Design,'' \textit{Trans. on VLSI}, Nov. 2006.

\bibitem{huang_tc2008} Huang et al., ``Accurate, Pre-RTL Temperature-Aware Design Using a Parameterized, Geometric Thermal Model,'' \textit{Trans. on Computers}, Sept. 2008.

\bibitem{kahng_date2009} Kahng et al., ``Orion 2.0: A Fast and Accurate NoC Power and Area Model for Early-Stage Design Space Exploration,'' \textit{DATE}, Apr. 2009.

\bibitem{li_micro2009} Li et al., ``McPAT: Integrated Power, Area, Timing Modeling Framework for Multicore Architectures,'' \textit{MICRO}, Dec. 2009. 

\bibitem{rosenfeld_cal2011} Rosenfeld et al., ``DRAMsim2: A Cycle Accurate Memory System Simulator,'' \textit{Computer Architecture Letters}, Jan. 2011.

\bibitem{sridhar_iccad2010} Sridhar et al., ``3D-ICE: Fast Compact Transient Thermal Modeling for 3D ICs with Inter-Tier Liquid Cooling,'' \textit{ICCAD}, Nov. 2010. 

\bibitem{srinivasan_isca2004} Srinivasan et al., ``The Case for Lifetime Reliability-Aware Microprocessors,'' \textit{ISCA}, June 2004.

\bibitem{srinivasan_micro2005} Srinivasan et al., ``Lifetime Reliability: Toward An Architectural Solution,'' \textit{IEEE Micro}, May 2005. 

\bibitem{sun_nocs2012} Sun et al., ``DSENT - A Tool Connecting Emerging Photonics with Electronics for Opto-Electronic Networks-on-Chip Modeling,'' \textit{NOCS}, May 2012.

\bibitem{thoziyoor_isca2008} Thoziyoor et al., ``A Comprehensive Memory Modeling Tool and Its Application to The Design and Analysis of Future Memory Hierarchies,'' \textit{ISCA}, June 2008.

\bibitem{white_jpl2008} White et al., ``Microelectronics Reliability: Physics-of-Failure Based Modeling and Lifetime Evaluation,'' \textit{NASA JPL Publication}, 2008. 

\end{thebibliography}
